Reproducible Results- Project #1
================================
## 1
Set working director and download/unzip applicable files
```{r echo=TRUE}
#setwd("RR")
#download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip","activity.zip")
#unzip("activity.zip")
activity <- read.csv("activity.csv")
```

## 2
Sum the steps per day and create associated histogram
```{r echo=TRUE}
stepsPerDay <- aggregate(activity$steps, by=list(date=activity$date),FUN=sum)
names(stepsPerDay) = c("Date", "StepsPerDay")
hist(stepsPerDay$StepsPerDay, breaks=nrow(stepsPerDay), main="Histogram Step Counts Per Day", xlab="Step Counts Per Day")
```

## 3
Mean and Medians:
```{r echo=TRUE}
mean(stepsPerDay$StepsPerDay, na.rm=TRUE)
median(stepsPerDay$StepsPerDay, na.rm=TRUE)
```

## 4
Time series plot
```{r echo=TRUE}
fiveMinInterval <- aggregate(activity$steps, by=list(interval=activity$interval),FUN=mean, na.rm=TRUE)
names(fiveMinInterval) = c("interval","averageStepsPerDay")
plot(fiveMinInterval$interval, fiveMinInterval$averageStepsPerDay, type="l", main="Average Steps Per Interval At Each Day", xlab="interval", ylab="average each day")
```

## 5
Interval with maximum average
```{r echo=TRUE}
fiveMinInterval[which.max(fiveMinInterval$averageStepsPerDay),1]
```

## 6
Replace missing data with average of all others prior to replacing NA's:
Number of NA rows:
```{r echo=TRUE}
NArows <- nrow(is.na(activity$steps))
```

Replace NA rows with average of others and store in new database
```{r echo=TRUE}
averageNonMissing <- mean(activity$steps, na.rm=TRUE)
tempActivity <- activity
tempActivity[,1] <- ifelse(is.na(activity$steps),averageNonMissing, activity$steps)
```

## 7
Sum the new steps per day and create associated histogram
```{r echo=TRUE}
newstepsPerDay <- aggregate(activity$steps, by=list(date=activity$date),FUN=sum)
names(newstepsPerDay) = c("Date", "StepsPerDay")
hist(newstepsPerDay$StepsPerDay, breaks=nrow(newstepsPerDay), main="New Histogram Step Counts Per Day", xlab="Step Counts Per Day")
```

New Mean and Medians:
```{r echo=TRUE}
mean(newstepsPerDay$StepsPerDay, na.rm=TRUE)
median(newstepsPerDay$StepsPerDay, na.rm=TRUE)
```
Do these values differ from the estimates from the first part of the assignment?  **Yes**  
What is the impact of imputing missing data on the estimates of the total daily number of steps? **Estimates increase**

## 8
Restart array and sort weekdays from weekends and panel plots
```{r echo=TRUE}
library(ggplot2)
newActivity <- read.csv("activity.csv")
newActivity$date <- as.Date(newActivity$date,"%Y-%m-%d")

newActivity[,"weekday_end"] <- ifelse(weekdays(newActivity$date) %in% c("Saturday","Sunday"),"weekend","weekday")

fiveMinInterval <- aggregate(newActivity$steps, by=list(interval=newActivity$interval, weekday_end=newActivity$weekday_end),FUN=mean, na.rm=TRUE)

ggplot(fiveMinInterval) + geom_line(aes(x=interval, y=x)) + facet_grid(rows = "weekday_end") + labs(y="Average Number of Steps", x="Interval")
```